A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828

### 2018-09-09 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
	   label_size = 25,	   
           hjust = -1,
           nrow = 1
           )

>>>>

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none") + ylim(c(0, 7)),
           pics[[2]] + theme(legend.position="none") + ylim(c(0, 7)),
           align = 'vh',
           labels = c("A", "B"),
	   label_size = 25,	   
           hjust = -1,
           nrow = 1
           )
